Start with the literature: assessthe empirical evidence for the relationship between ter-rorism and political attitudes

### 2024-02-15 outputs/paper/paper.qmd
edits

The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @table-t. @table-t displays the estimated overall correlations ($Z_r$). The correlations in this table are Fisher's Z-transformed, while those reported in the text below are back-transformed to their normal correlation scale (denoted as $\widehat{\rho}$) for ease of interpretation[@main_paper].

```{r}
#| label: table-t
#| tbl-cap: "Note. k = number of effect sizes. j = number of manuscripts. Zr = Overall Fisher's Z correlation coefficients. LBCI = Likelihood-Based Confidence Interval. The Zr estimates are considered significant when the LBCIs do not include zero."
#| echo: false
#| message: false
#| warning: false

@@

@table-t shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090). @main_paper indicates that it is important to note that all associations are relatively small, both following conventional standards and compared to other meta-analyses in the social sciences.

>>>>

The extent of terrorism's association with outgroup hostility, political conservatism, or rally-'round-the-flag responses can be observed in the estimated overall correlations ($Z_r$) displayed in @tbl-t. @tbl-t displays the estimated overall correlations ($Z_r$). The correlations in this table are Fisher's Z-transformed, while those reported in the text below are back-transformed to their normal correlation scale (denoted as $\widehat{\rho}$) for ease of interpretation[@main_paper].

```{r}
#| label: tbl-t
#| tbl-cap: "Note. k = number of effect sizes. j = number of manuscripts. Zr = Overall Fisher's Z correlation coefficients. LBCI = Likelihood-Based Confidence Interval. The Zr estimates are considered significant when the LBCIs do not include zero."
#| echo: false
#| message: false
#| warning: false

@@

@tbl-t shows that terrorism is significantly associated with outgroup hostility ($\widehat{\rho}$ = 0.126), political conservatism($\widehat{\rho}$ = 0.131), and, to a lesser extent, rally-‘round-the-flag effects ($\widehat{\rho}$ = 0.090). @main_paper indicates that it is important to note that all associations are relatively small, both following conventional standards and compared to other meta-analyses in the social sciences.
